Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-11 paper/paper.tex
pass on step 3

\tname{} uses a composition of heurisitc functions to sort the rules
it produces. Each function uses a different criterion to estimate how
similar a rule created in the previous step is to existing Suricata
rules~\cite{emerging-threats-open}. We describe in the following each
of these heuristic functions. Each function $f_i$ ranges in the 0-1
domain. \tname{} uses the weighted average of these functions to sort
rules: $\sum{f_i}/|f_i|$.

\subsubsection{Size of a rule}
\tname{} uses the size of existing rules as a heuristic function. For
example, we noted that most rules in the dataset have 2 to 5 options,
so \tname{} values rules in this size range higher compared to other
sizes. Figure~\ref{fig:distribution-rule-size} shows the histogram of
rule sizes. The x-axis shows the number of options (\ie{}, size)
included in a rule and the y-axis shows the number of rules that have
that number of options. \tname{} uses this information to rank rules.

@@

\Mar{----------------------------------------- estou aqui}

Regras com um tamanho mais comum pontuam mais.
Nesse caso, a pontuação dada por esse componente será: \[\frac{rules\_per\_size[len(rule)]}{max(rules\_per\_size)}\]

>>>>

\tname{} uses a composition of heurisitc functions to sort the rules
it produces. Each function uses a different criterion to estimate how
similar a rule, created in the previous step, is to existing Suricata
rules~\cite{emerging-threats-open}. We describe in the following each
of these heuristic functions. Each function $f_i$ ranges in the 0-1
domain. \tname{} uses the weighted average of these functions to sort
rules: $\sum{f_i}/|f_i|$.

\subsubsection{Size of a rule}
\tname{} uses the size of existing rules as one element to measure
similarity. Informally, rules with popular sizes score high; inpopular
rules score low.

Figure~\ref{fig:distribution-rule-size} shows the histogram of rule
sizes for our rule dataset, including a total of
\numrulessuri\ rules. The x-axis shows the number of options included
in a rule and the y-axis shows the number of rules with the
corresponding number of options. For example, we noted that most rules
have 2 to 6 options. Based on that, \tname{} values rules in that size
range higher compared to other sizes.

%\tname{} uses this information to rank rules.

@@

More precisely, we calculate the contribution of size of a given rule
$r$ with the following formula:

\[\frac{\mathit{rules\_per\_size}[\mathit{len(r)}]}{\mathit{num\_rules}}\]

\noindent
, where $\mathit{len(r)}$ denotes the number of options of a rule $r$,
$\mathit{rules\_per\_size}$ encodes the size distribution--it is a
dictionary mapping the number of rules associated with a given size,
and $\mathit{num\_rules}$ returns the number of elements in the
dictionary. Consequently, the contribution of size is proportion;al to
its popularity. For example, the contribution of this heuristic for a
rule with 3 options would be 0.145 (=3,662/25,239) whereas the
contribution of a rule with 9 options would be 0.03 (=763/25,239).

\Mar{--------------------------- estou aqui}
